\documentclass{article}
\usepackage[utf8]{inputenc}

\title{wizeUp}
\author{Supervisor: Dr. Amit Dvir}
\author{Shay Cohen, Damir Bar, Eran Sterman, Dima Volgin , Sefi Shalom}

\begin{document}

\maketitle

\section{Introduction}

Over the passed hundred years, the educational system never evolved. By the 00' it improved massively by using a wide range of different services and applications to ease the learning experience, such as: 
\begin{itemize}
\item WhatsApp, Facebook - Forum/messaging tools for group chatting, messy file sharing system and Q&A.
\item Google Drive, Dropbox - Generic not student-oriented cloud system.
\itemMoodle - Old communication system between students and lecturers, an exercise submittion feature and Q&A option.
\item Gool - Non-free on-demand video courses.
\item Kahoot - Interactive student teacher app.
\item Institution based feedback.
\end{itemize}
\textbf{wizeUp}  is a reality which combines and enhances these features and more in to one easy-to-use user-friendly platform.

\textbf{You are our audience if you}:
\begin{itemize}
\item Study in the academy.
\item Are a lecturer/T.A in the academy.
\item Are an undergraduate student.
\item Teach in any sort of framework.  
\item Take part in any private educational system outside the academy.
\item Want to overcome your educational potential using the best platform in the world.
\end{itemize}
So how do we do this?\\
\textbf{wizeUp}  allows teachers to upload relevat files, answer students' questions  and improve their teaching methods using \textbf{wizeUp}  feedback. With \textbf{wizeUp}  students can communicate with their classmates, share files and enjoy live video streaming, providing the option of live feedback. \textbf{wizeUp}  is the best way to gather statistical information for the use of both parties, students and teachers, as well as any department chosen. \textbf{wizeUp}  will drive both sides, students and teachers, to thrive using a scoring system. \textbf{wizeUp}  will make teaching and learning easier, faster and better.

\section{Features}

\begin{itemize}
\item User Experience: 
\begin{itemize}
\item Live stream video
\item Tracking course progress
\item \textbf{wizeUp} annual extraordinary
\end{itemize}
\item User convenience
\begin{itemize}
\item Grades & Average calculator
\item File system
\item Q&A
\item Student answer providing instead of teacher
\item Android/IOS/Web UI
\item Messaging system
\end{itemize}
\item Statistical collection
\begin{itemize}
\item Live feedback
\item Fame system
\item Scoring system
\end{itemize}
\item Security
\begin{itemize}
\item Spamming/Abusive user reporting system
\item Anonymity option 
\item General security
\end{itemize}
\item Accessibility 
\begin{itemize}
\item Multiple language support
\end{itemize}
\end{itemize}
\end{document}
